Type Refinements for the Working Class

### 2015-12-23 paper.tex
no need to even show the Match operator
Add Base{τ} type

@@

Fix an extensional lcs whose signature contains the following:
\[
  \infer{
    \IsSort{\SortAtom}
  }{
  }
\]
\[
  \infer{
    \IsCanOperator{\Upsilon,a:\SortAtom}{
      \OpToken{a}
    }{
      \MkArity{}{\SortAtom}
    }
  }{
  }
  \qquad
  \infer{
    \IsOperator{\Upsilon}{
      \OpMatch{\tau}
    }{
      \MkArity{
        \MkValence{}{}{\SortAtom};
        \MkValence{}{}{\tau};
        \MkValence{}{}{\tau}
      }{\tau}
    }
  }{
    \IsSort{\tau}
  }
\]

>>>>

\subsubsection{The type of closed expressions}

The \emph{discrete} refinement on a sort (which equates each closed term only
with itself, up to alpha equivalence) is not a type in general, because it may
not respect computational equivalence. However, we can form the next best
thing, which is called the \emph{base} refinement, which identifies closed
expressions of a sort up to computational equivalence.

Let $\GloballyRefines{\TyBase{\tau}}{\tau}$ for any sort $\tau$ be defined as
follows:
\[
  \infer{
    \RMemEq{\Upsilon}{M}{N}{\TyBase{\tau}}
  }{
    \PBinRel{\sim_\tau}{\Upsilon}{M}{N}
  }
\]

Then, we clearly have $\IsType{\Upsilon}{\TyBase{\tau}}{\tau}$, because it respects
computational equivalence by definition.

@@

Fix an extensional lcs whose signature contains the following:
\[
  \infer{
    \IsSort{\SortAtom}
  }{
  }
  \qquad
  \infer{
    \IsCanOperator{\Upsilon,a:\SortAtom}{
      \OpToken{a}
    }{
      \MkArity{}{\SortAtom}
    }
  }{
  }
\]
